\newpage
\setcounter{page}{1}
\lhead{Pad}
\lfoot{\thepage / \pageref{end_section_pressurant}}
\section*{Pad}
\input{0_NoteMissionControl}
\input{0_Legend}

IF A CHECK FAILS AND NO OTHER MEASURE IS SPECIFIED OR THE SPECIFIED MEASURE FAILS TOO, INFORM LEAD AND AWAIT FURTHER INSTRUCTIONS

\begin{enumerate}[label=P\arabic*.]

    \item READ THE WHOLE CHECKLIST BEFORE STARTING \checkbox

    \starttask{Required tools, materials and personnel}{\hphantom{a}}
    \item \label{pad_personnel} Personnel
        \begin{enumerate}[label*=\arabic*.]
            \item Pad 1: Daniel Frank
            \item Pad 2: Michael Pohn
            \item Pad 3: Florian Dellekart
            \item Pad 4: Bernhard Hansemann
            \item Documentation: Liana Gferer
        \end{enumerate}
    \item \label{pad_tools} Tools \checkbox
        \begin{enumerate}[label*=\arabic*.]
            \item Hammer\leftcheckbox
            \item T10 Key\leftcheckbox
            \item T30 Key\leftcheckbox
            \item Allen Key \SI{2.5}{\milli\meter}\leftcheckbox
            \item Ethanol Fueling Syringe\leftcheckbox
            \item Tweezers\leftcheckbox
            \item Fire extinguisher\leftcheckbox
        \end{enumerate}
    \item \label{pad_materials} Materials \checkbox
        \begin{enumerate}[label*=\arabic*.]
            \item Red pendant\leftcheckbox
            \item Ice or dry ice (min. \SI{3}{\kilo\gram})
            \item Oxidizer bottle mounting plate\leftcheckbox
            \item Heat exchanger tube\leftcheckbox
            \item Oxidizer Bottle\leftcheckbox
            \item Ethanol Bottles (\SI{2}{\liter})\leftcheckbox
            \item Flame Diverter\leftcheckbox
            \item Rocket (without fincan)\leftcheckbox
            \item Fincan\leftcheckbox
            \item 8x black M4 screws(4x8 mm, 4x10 mm) for fincan \leftcheckbox
            \item RBF umbilical locking device \leftcheckbox
            \item TRS-box (ALWAYS stays with rocket) \leftcheckbox
        \end{enumerate} 
    
    \starttask{On-day pad prep}{\hphantom{a}}
    \item \label{pad_on_day_start} If not already at correct position, place trailer at final launch site.\checkbox
    \item Recheck position and angles of launch rail and realign if necessary.\checkbox
    \item Voice radio check with MC. \checkbox
    \item Open server rack and remove cover from bottom air intake.\checkbox
    \item Remove masking tape from cable outlet at the back.\checkbox
    \item Connect server rack power distributor to power.\checkbox
    \item Set up pad cams if not already done. \checkbox
    \item Verify that all Ethernet and power cables are connected correctly.\checkbox
    \item Start server if not already starting automatically.\checkbox
    \item Start heating hot water reservoir.\checkbox
    \item Start cooling cold water reservoir, refill ice periodically until \ref{vacate_pad}.\checkbox
    \item Place oxidizer bottle next to trailer \checkbox
    \item Install mounting plate on oxidizer bottle \checkbox
    \item Install Ox bottle on tanking cart \checkbox
    \item Install heat exchanger on oxidizer bottle \checkbox
    \item Connect water hoses to heat exchanger\checkbox
    \item Install Pressurant bottle\checkbox
    \item Install flame diverter\checkbox
    \item Report on-day pad preparation complete to Mission Lead\checkbox
    
    \starttask{On-day electronics check}{\hphantom{a}}
    \item \label{pad_on_day_elec_start} Wait for MC to start aligning directed radio link.\checkbox
    \item \underline{MC: check functionality of following individual sensors,}\newline\underline{no software errors}
      \begin{enumerate}[label*=\arabic*.]
            \item Hot water temperature \leftcheckbox
            \item Cold water temperature \leftcheckbox
            \item Mantle water temperature \leftcheckbox
            \item Pressurant pressure \leftcheckbox
            \item Ox pressure \leftcheckbox
      \end{enumerate}
  \item \underline{MC:
    check functionality of actuators (verify movement and calibration)}
    \newline\underline{Software reports no errors and visual inspection of actuator movement}
      \begin{enumerate}[label*=\arabic*.]
            \item Ox tanking valve \leftcheckbox
            \item Ox vent valve \leftcheckbox
            \item Pressurant tanking valve \leftcheckbox
            \item Pressurant vent valve \leftcheckbox
            \item Umbilical retract \leftcheckbox
            \item Clean water pump intake filters \leftcheckbox
            \item Hot water pump \leftcheckbox
            \item Cold water pump \leftcheckbox
            \item Holddown \leftcheckbox
      \end{enumerate}
    
    \item Report On-Day electronics check complete to Mission Lead.\checkbox
    \item \label{pad_on_day_elec_end} Vacate area.\checkbox
    
    \starttask{Rocket mounting}{\hphantom{a}}
    \item \label{pad_rocket_mounting_start} Pad 1 \& 2 get rocket, fincan and TRS-box to pad.\checkbox
    \item Remove sliding block from launch rail.\checkbox
    \item Verify holddown open, if not request MC to open it.\checkbox
    \item Slide rocket (without fincan) onto rail (from bottom).\checkbox
    \item Secure rocket with sliding block underneath lower rail button.\checkbox
    \item Secure holddown above lower rail button.\checkbox
    \item Verify holddown is closed and locked.\checkbox
    \item Swivel strongback into position \checkbox
    \item Attach RBF umbilical locking device \checkbox
    \item Remove cover from pressurant loading ports.\checkbox
    \item Connect Ox pressurant umbilical.\checkbox
    \item Connect Fuel pressurant umbilical.\checkbox
    \item Verify pressurant umbilicals' mechanical connection (pull umbilical), reconnect if loose\checkbox
    \item Connect Electrical umbilical and secure with masking tape.\checkbox
    \item \underline{Request active charging.}\checkbox
    \item Pull RBF Pin halfway\checkbox
    \item Cover rocket in space blanket\checkbox
    \item \label{pad_rocket_mounting_end} Report rocket mounting completed to Mission Lead\checkbox
    
    \starttask{Fueling}{\hphantom{a}}
    \item \label{pad_fueling_start} Wait for fueling request from Lead.\checkbox
    \item Verify fuel main valve is closed.\checkbox
    \item Fill fueling syringe with \SI{950}{\milli\liter} ethanol\checkbox
    \item Fuel \SI{900}{\milli\liter} \checkbox
    \item Clean up spills\checkbox
    \item Mount fincan to rocket\checkbox
    \item Secure fincan with 8 screws\checkbox
    \item Remove cover from oxidizer loading port\checkbox
    \item Connect Ox umbilical\checkbox
    \item Verify Ox umbilical mechanical connection (pull umbilical), reconnect if loose\checkbox
    \item \label{pad_fueling_end} Report that fueling is completed to Mission Lead.\checkbox

    \starttask{Final Preps}{\hphantom{a}}
    \item \label{pad_final_preps_start} Wait for Mission Lead to request Final Preps\checkbox
    \item Unfold emergency umbilical release line and extend \newline line away from pad \checkbox
    \item Clean intake filters for water pumps \checkbox
    \item Put on safety glasses, gloves, hearing protection and long sleeved shirt and trousers.\checkbox
    \item Verify holddown closed\checkbox
    \item Start pad cams\checkbox
    \item Request Pressurization clearance from EuRoC LCO\checkbox
    \item Raise red pendant\checkbox
    \item \label{open_ox} Open Ox bottle\checkbox
    \item Check for leaks (feel for air current on connections), if found inform Mission Lead, close bottle, retighten connection and goto \ref{open_ox}\checkbox
    \item \label{open_press} Open Pressurant bottle\checkbox
    \item Check for leaks (feel for air current on connections), if found inform MC, close bottle, retighten connection and goto \ref{open_press}\checkbox
    \item Read out pressurant bottle pressure and forward to Mission Lead.\checkbox
    \item Start flight on TRS\checkbox
    \item Remove RBF zip tie \checkbox
    \item Remove RBF umbilical locking device \checkbox
    \item Pull RBF pin\checkbox
    \item Report Final preps complete to Mission Lead.\checkbox
    \item \label{vacate_pad} Vacate pad\checkbox
    
    \starttask{GSE Safing}{\hphantom{a}}
    \item \label{pad_gse_safing_start} Verify no heat sources except heating element\checkbox
    \item Close Ox bottle\checkbox
    \item Close Pressurant bottle.\checkbox
    \item Unplug heating element.\checkbox
    \item Verify heating cycle is deactivated.\checkbox
    \item \label{pad_gse_safing_end} Vacate area.\checkbox
    \item Report GSE Safing done to Mission Lead.\checkbox

    
\label{end_section_pressurant}
\end{enumerate}